Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2022-05-02 UMich/chapters/ch02-WPProdPerf.tex
Move proposal content into UMich template.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=3in]{fig/WPProdPerf/fig-knitting.png}
\caption{
From Wikipedia {\em Knitting} talk page.
Two WikiProjects have assessed the article as B-class quality.
\label{fig:knitting}
}
\end{center}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=2.5in,height=2.5in]{fig/WPProdPerf/fig-eff-perf-hist.pdf}
\caption{
Histograms of WikiProject productivity and performance.
Both measures are highly right-skewed, but form unimodal distributions
with low skewness after log transformation.
\label{fig:eff-perf-hist}
}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=3in]{fig/WPProdPerf/fig-perf-prod}
\caption{
WikiProject performance is anticorrelated with B-level productivity,
with Pearson r of -0.12.
Results are similar for other grade levels.
On average, highly productive WikiProjects are under-performing,
but when looking at specific WikiProjects,
some are higher than others in both performance and productivity.
\label{fig:eff-perf}
}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=2.33in,height=2.33in]{fig/WPProdPerf/fig-degree-mincut.pdf}
%\caption{
%Min-cut of WikiProject coeditor networks vs. their mean degree.
%\label{fig:degree-mincut}
%}
%\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=3in,height=1.5in]{fig/WPProdPerf/fig-val-iter.pdf}
\caption{
Mean agent solution value over time, averaged over 100 trials.
Strategies are defined in Table \ref{tab:strat}.
\label{fig:val-iter}
}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{fig/WPProdPerf/fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{fig/WPProdPerf/fig-deg-perf.pdf}
\caption{
productivity and Performance of social learning strategies vs. mean network degree.
Each point represents a single trial of 300 iterations.
Strategies are defined in Table \ref{tab:strat}.
The local best-neighbor strategy shows
decreased performance at high degree,
with no significant change in productivity.
Local conformity shows decreased performance and increased productivity at high
degree.
Local majority shows the opposite behavior:
increased performance and decreased productivity at high degree,
with the productivity showing the largest effect size of all strategies.
\label{fig:deg-eff-perf}
}
\end{figure*}

>>>>

\begin{figure}[t!]
\begin{center}
\includegraphics[width=3in]{chapters/figures/WPProdPerf/fig-knitting.png}
\caption{
From Wikipedia {\em Knitting} talk page.
Two WikiProjects have assessed the article as B-class quality.
\label{fig:knitting}
}
\end{center}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=2.5in,height=2.5in]{chapters/figures/WPProdPerf/fig-eff-perf-hist.pdf}
\caption{
Histograms of WikiProject productivity and performance.
Both measures are highly right-skewed, but form unimodal distributions
with low skewness after log transformation.
\label{fig:eff-perf-hist}
}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=3in]{chapters/figures/WPProdPerf/fig-perf-prod}
\caption{
WikiProject performance is anticorrelated with B-level productivity,
with Pearson r of -0.12.
Results are similar for other grade levels.
On average, highly productive WikiProjects are under-performing,
but when looking at specific WikiProjects,
some are higher than others in both performance and productivity.
\label{fig:eff-perf}
}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=2.33in,height=2.33in]{chapters/figures/WPProdPerf/fig-degree-mincut.pdf}
%\caption{
%Min-cut of WikiProject coeditor networks vs. their mean degree.
%\label{fig:degree-mincut}
%}
%\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=3in,height=1.5in]{chapters/figures/WPProdPerf/fig-val-iter.pdf}
\caption{
Mean agent solution value over time, averaged over 100 trials.
Strategies are defined in Table \ref{tab:strat}.
\label{fig:val-iter}
}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{chapters/figures/WPProdPerf/fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{chapters/figures/WPProdPerf/fig-deg-perf.pdf}
\caption{
productivity and Performance of social learning strategies vs. mean network degree.
Each point represents a single trial of 300 iterations.
Strategies are defined in Table \ref{tab:strat}.
The local best-neighbor strategy shows
decreased performance at high degree,
with no significant change in productivity.
Local conformity shows decreased performance and increased productivity at high
degree.
Local majority shows the opposite behavior:
increased performance and decreased productivity at high degree,
with the productivity showing the largest effect size of all strategies.
\label{fig:deg-eff-perf}
}
\end{figure*}

### 2022-05-02 UMich/chapters/ch03-NetDelibABM.tex
Move proposal content into UMich template.

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-broadcast.eps}
    \caption{Mean time necessary for a signal broadcast from one node to reach the entire network. We use mean broadcast time as a measure of geodesic length for time-varying networks.}
    \label{fig:broadcast}
\end{figure}

@@

\begin{figure*}[]
    \label{fig:results}
    \centering
    \begin{minipage}{3.33in}
        \centering
        \includegraphics[width=3.33in]{fig/NetDelibABM/fig-perf-both.eps}
    \end{minipage}%
    \begin{minipage}{1.875in}
    \centering
    \includegraphics[width=1.875in]{fig/NetDelibABM/fig-converge-both.eps}
    \end{minipage}
\caption{
Solution quality and convergence time for agent-based simulations of different learning strategies. Error bars represent 95\% confidence interval. Results for network deliberation are shown shaded.
}
\end{figure*}

\begin{figure}
    \label{fig:results-frac-parallel}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for parallel individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-frac-fallback}
    \centering
%    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for fallback individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-bn-parallel-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-cn-parallel-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-conf-parallel-dist.eps}
\caption{Solution quality distribution for the conform strategy with parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-bn-fallback-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-cn-fallback-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-conf-fallback-dist.eps}
\caption{Solution quality distribution for the conform strategy with fallback individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-conform-diff}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-results-netdelib-diff.eps}
\caption{Difference in solution quality between network deliberation and conventional deliberation. Plots for Best/Confident-Neighbor show results for long-path and small-world networks, while the plot for conform shows results for random-pod and preferential-attachment networks. Results are shown for parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-conform-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-results-conform-dist.eps}
\caption{Distributions of solution quality for social learning on a preferential-attachment network and random-pod network deliberation. Results are shown for parallel individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-netdelib-efficiency}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-results-netdelib-efficiency.eps}
\caption{Difference in solution quality between random-pod (efficient) and long-path (inefficient) network. Results are shown for parallel individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-confident}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-results-confident.eps}
\caption{Histograms of the difference in solution quality between confident-neighbor and best-neighbor for both conventional networks.
Results are shown for parallel individual learning.}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-broadcast.eps}
    \caption{Mean time necessary for a signal broadcast from one node to reach the entire network. We use mean broadcast time as a measure of geodesic length for time-varying networks.}
    \label{fig:broadcast}
\end{figure}

@@

\begin{figure*}[]
    \label{fig:results}
    \centering
    \begin{minipage}{3.33in}
        \centering
        \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-perf-both.eps}
    \end{minipage}%
    \begin{minipage}{1.875in}
    \centering
    \includegraphics[width=1.875in]{chapters/figures/NetDelibABM/fig-converge-both.eps}
    \end{minipage}
\caption{
Solution quality and convergence time for agent-based simulations of different learning strategies. Error bars represent 95\% confidence interval. Results for network deliberation are shown shaded.
}
\end{figure*}

\begin{figure}
    \label{fig:results-frac-parallel}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for parallel individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-frac-fallback}
    \centering
%    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for fallback individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-parallel-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-parallel-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-parallel-dist.eps}
\caption{Solution quality distribution for the conform strategy with parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-fallback-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-fallback-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-fallback-dist.eps}
\caption{Solution quality distribution for the conform strategy with fallback individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-conform-diff}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-results-netdelib-diff.eps}
\caption{Difference in solution quality between network deliberation and conventional deliberation. Plots for Best/Confident-Neighbor show results for long-path and small-world networks, while the plot for conform shows results for random-pod and preferential-attachment networks. Results are shown for parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-conform-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-results-conform-dist.eps}
\caption{Distributions of solution quality for social learning on a preferential-attachment network and random-pod network deliberation. Results are shown for parallel individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-netdelib-efficiency}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-results-netdelib-efficiency.eps}
\caption{Difference in solution quality between random-pod (efficient) and long-path (inefficient) network. Results are shown for parallel individual learning.}
\end{figure}

@@

\begin{figure}
    \label{fig:results-confident}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-results-confident.eps}
\caption{Histograms of the difference in solution quality between confident-neighbor and best-neighbor for both conventional networks.
Results are shown for parallel individual learning.}
\end{figure}

### 2022-05-02 UMich/chapters/ch04-NetDelibExp.tex
Move proposal content into UMich template.

\begin{figure}
\label{fig:reply}
\center
\frame{\includegraphics[width=5in]{fig/Experiment/fig-reply.png}}
\caption{Participants can perform standard forum actions, such as posting and commenting.}
\end{figure}

\begin{figure}
\label{fig:vote}
\center
\frame{\includegraphics[width=3in]{fig/Experiment/fig-vote.png}}
\caption{Participants are presented with a ranked-choice voting screen between rounds of deliberation.}
\end{figure}

\begin{figure}
\label{fig:alias}
\center
\frame{\includegraphics[width=3in]{fig/Experiment/fig-alias.png}}
\caption{Participants are assigned an alias for the duration of the experiment.}
\end{figure}

@@

\begin{figure}
\label{fig:kcon}
\includegraphics[width=5in]{fig/Experiment/fig-kcon.eps}
\caption{The k-connectivity of long-path and random-pod network deliberation
networks for $T=3$ stages and a pod size of $M=5$.}
\end{figure}

>>>>

\begin{figure}
\label{fig:reply}
\center
\frame{\includegraphics[width=5in]{chapters/figures/Experiment/fig-reply.png}}
\caption{Participants can perform standard forum actions, such as posting and commenting.}
\end{figure}

\begin{figure}
\label{fig:vote}
\center
\frame{\includegraphics[width=3in]{chapters/figures/Experiment/fig-vote.png}}
\caption{Participants are presented with a ranked-choice voting screen between rounds of deliberation.}
\end{figure}

\begin{figure}
\label{fig:alias}
\center
\frame{\includegraphics[width=3in]{chapters/figures/Experiment/fig-alias.png}}
\caption{Participants are assigned an alias for the duration of the experiment.}
\end{figure}

@@

\begin{figure}
\label{fig:kcon}
\includegraphics[width=5in]{chapters/figures/Experiment/fig-kcon.eps}
\caption{The k-connectivity of long-path and random-pod network deliberation
networks for $T=3$ stages and a pod size of $M=5$.}
\end{figure}
